### 2020-05-01 final_report/conclusion.tex
Final QASS results and plots.

After a thorough review of the literature, we developed a novel adaptive
sampling algorithm, QASS, capable of interfacing with any of the studied
surrogates. Preliminary testing on a toy theory, qualitatively comparable to
the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends
consistent with the design of the algorithm. With~\num{100000} initial samples and 100 incremental samples per iteration, QASS achieved a ${\sim}60\%$ decrease in surrogate error as compared with a baseline random sampling scheme. Equivalently, the same surrogate error as the baseline could be achieved with ${\sim}6\%$ fewer total samples of the expensive theory. Further optimisation over the hyperparameter space has strong
potential to increase this performance, in particular by decreasing the required quantity of initial samples. This will allow for future deployment of QASS
in coalition with any of the most effective identified surrogates to facilitate
learning during evaluation of the MC TBR model.

>>>>

After a thorough review of the literature, we developed a novel adaptive
sampling algorithm, QASS, capable of interfacing with any of the studied
surrogates. Preliminary testing on a toy theory, qualitatively comparable to
the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends
consistent with the design of the algorithm. With~\num{100000} initial samples and 100 incremental samples per iteration, QASS achieved a ${\sim}40\%$ decrease in surrogate error as compared with a baseline random sampling scheme. Equivalently, the same surrogate error as the baseline could be achieved with ${\sim}6\%$ fewer total samples of the expensive theory. Further optimisation over the hyperparameter space has strong
potential to increase this performance, in particular by decreasing the required quantity of initial samples. This will allow for future deployment of QASS
in coalition with any of the most effective identified surrogates to facilitate
learning during evaluation of the MC TBR model.

### 2020-05-01 final_report/results.tex
Final QASS results and plots.

Such tests revealed that while QASS has unmatched performance on its own
adaptively-sampled training set, it is outperformed by the baseline scheme on
uniformly-random evaluation sets. We suspected that while QASS excels in
learning the most strongly peaked regions of the TBR theory, this comes at the
expense of precision in broader, smoother regions where uniformly random
sampling suffices. Therefore a mixed scheme was implemented, with half MCMC
samples and half uniformly random samples incremented on each iteration, which
is also shown in~\cref{fig:qasssampling}. An increase in initial sample size was observed to also resolve precision in these smooth regions of the toy theory, as the initial samples were obtained from a uniform random distribution. As shown in ~\cref{fig:qasssampling100k}, with~\num{100000} initial samples it was possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline scheme. Comparing at the point of termination for QASS, this corresponds to a ${\sim}6\%$ decrease in the number of total samples needed to train a surrogate with the same error.

>>>>

Such tests revealed that while QASS has unmatched performance on its own
adaptively-sampled training set, it is outperformed by the baseline scheme on
uniformly-random evaluation sets. We suspected that while QASS excels in
learning the most strongly peaked regions of the TBR theory, this comes at the
expense of precision in broader, smoother regions where uniformly random
sampling suffices. Therefore a mixed scheme was implemented, with half MCMC
samples and half uniformly random samples incremented on each iteration, which
is also shown in~\cref{fig:qasssampling}. An increase in initial sample size was observed to also resolve precision in these smooth regions of the toy theory, as the initial samples were obtained from a uniform random distribution. As shown in ~\cref{fig:qasssampling100k}, with~\num{100000} initial samples it was possible to obtain a ${\sim}40\%$ decrease in error as compared to the baseline scheme, from 0.0025 to 0.0015 mean averaged error. Comparing at the point of termination for QASS, this corresponds to a ${\sim}6\%$ decrease in the number of total samples needed to train a surrogate with the same error.
